---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
`teachboostr` is a simple R package that provides bindings to the TeachBoost API.

### Getting Started

The package is only available on github:
```{r, eval=FALSE}
devtools::install_github('kippchicago/teachboostr')
```

`get_tb()` is a wrapper around the workhourse `teachboost_api()` function. If you save your API key in an `.Renviron` file with the variable name `KEY_TB` the `get_tb()` function will look it up; otherwise you should pass your key to the `key` parameter.

```{r, eval = FALSE}
library(teachboostr)

users <- get_tb("users")

users
```
You'll notice that `users` is a list of `teachboost_api` objects (which themselves are lists of the respons, content, and call).  This is result of the 1,000 record limit that TeachBoost imposes. The `get_tb()` function automates repining the api to get every record. 

You can use the `unpack_tb()` function to extract the content from the `get_tb` call:

```{r, eval=FALSE}
users_df <- unpack_tb(users)
```


Notice that nested JSON returned by the API will be stored as nested list-columns in the data frame.

